Reducing iptables configuration complexity using chains

### 2014-04-18 iptables/presentation.tex
remove leading iptables in config examples

      \small{iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport http -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      iptables -A INPUT -j DROP}

@@

      \small{iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      iptables -A INPUT -j DROP}

@@

      \small{iptables -P INPUT DROP\\
      iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      \sout{iptables -A INPUT -j DROP}}

@@

      \small{iptables -P INPUT ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT}

@@

      \small{iptables -P INPUT DROP\\
      iptables -P OUTPUT DROP\\
      iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT}

@@

      \small{iptables -P INPUT DROP\\
      iptables -P OUTPUT DROP\\
      iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      iptables -A OUTPUT -m tcp -p tcp --sport ssh -j ACCEPT\\
      iptables -A OUTPUT -m tcp -p tcp --sport 80 -j ACCEPT\\
      iptables -A OUTPUT -m tcp -p tcp --sport https -j ACCEPT}

@@

      \small{iptables -P INPUT DROP\\
      iptables -P OUTPUT DROP\\
      iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      iptables -A OUTPUT -m state --state ESTABLISHED,RELATED -j ACCEPT}

@@

@@

      \small{iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT}

@@

      \small{iptables -A INPUT -p tcp -m tcp -s 10.100.2.3 --dport 22 -j ACCEPT\\
      iptables -A INPUT -p tcp -m tcp -s 10.100.2.4 --dport 22 -j ACCEPT\\
      iptables -A INPUT -p tcp -m tcp -s 10.100.2.7 --dport 22 -j ACCEPT\\
      iptables -A INPUT -p tcp -m tcp -s 10.100.2.3 --dport 10000 -j ACCEPT\\
      iptables -A INPUT -p tcp -m tcp -s 10.100.2.4 --dport 10000 -j ACCEPT\\
      iptables -A INPUT -p tcp -m tcp -s 10.100.2.7 --dport 10000 -j ACCEPT}

@@

      \small{iptables -N admin\_IP\\

@@

      iptables -A admin\_IP -s 10.100.2.3 -j ACCEPT\\
      iptables -A admin\_IP -s 10.100.2.4 -j ACCEPT\\
      iptables -A admin\_IP -s 10.100.2.7 -j ACCEPT\\
      iptables -A admin\_IP -j DROP}

@@

      \small{iptables -A INPUT -p tcp -m tcp --dport 22 -j admin\_IP\\
      iptables -A INPUT -p tcp -m tcp --dport 10000 -j admin\_IP}

@@

      \small{iptables -N webmaster\_IP\\
      iptables -A webmaster\_IP -s 10.100.2.11 -j ACCEPT\\
      iptables -A webmaster\_IP -s 10.100.2.17 -j ACCEPT\\
      iptables -A webmaster\_IP -s 10.100.2.34 -j ACCEPT\\
      iptables -A webmaster\_IP -j DROP}

@@

      \small{iptables -A INPUT -p tcp -m tcp --dport 445 -j admin\_IP\\
      iptables -A INPUT -p tcp -m tcp --dport 445 -j webmaster\_IP\\
      iptables -A INPUT -p tcp -m tcp --dport 139 -j admin\_IP\\
      iptables -A INPUT -p tcp -m tcp --dport 139 -j webmaster\_IP}

@@

      \small{iptables -N webmaster\_IP\\
      iptables -A webmaster\_IP -s 10.100.2.11 -j ACCEPT\\
      iptables -A webmaster\_IP -s 10.100.2.17 -j ACCEPT\\
      iptables -A webmaster\_IP -s 10.100.2.34 -j ACCEPT\\
      \sout{iptables -A webmaster\_IP -j DROP}\\
      iptables -A webmaster\_IP -j admin\_IP}

@@

      \small{\sout{iptables -A INPUT -p tcp -m tcp --dport 445 -j admin\_IP}\\
      iptables -A INPUT -p tcp -m tcp --dport 445 -j webmaster\_IP\\
      \sout{iptables -A INPUT -p tcp -m tcp --dport 139 -j admin\_IP}\\
      iptables -A INPUT -p tcp -m tcp --dport 139 -j webmaster\_IP}

>>>>

      \small{-A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport http -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      -A INPUT -j DROP}

@@

      \small{-A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      -A INPUT -j DROP}

@@

      \small{-P INPUT DROP\\
      -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      \sout{-A INPUT -j DROP}}

@@

      \small{-P INPUT ACCEPT\\
      -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT}

@@

      \small{-P INPUT DROP\\
      -P OUTPUT DROP\\
      -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT}

@@

      \small{-P INPUT DROP\\
      -P OUTPUT DROP\\
      -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      -A OUTPUT -m tcp -p tcp --sport ssh -j ACCEPT\\
      -A OUTPUT -m tcp -p tcp --sport 80 -j ACCEPT\\
      -A OUTPUT -m tcp -p tcp --sport https -j ACCEPT}

@@

      \small{-P INPUT DROP\\
      -P OUTPUT DROP\\
      -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      -A OUTPUT -m state --state ESTABLISHED,RELATED -j ACCEPT}

@@

    \frametitle{Intermezzo : firewall on your PC}
    Protect your own PC, block all incoming requests :
      \small{-P INPUT DROP\\
      -P OUTPUT ACCEPT}\\
      \small{-A INPUT -i lo -j ACCEPT \# allow local traffic\\
      -A INPUT -p icmp -j ACCEPT \# allow ping\\
      -A INPUT -m state --state ESTABLISHED,RELATED -j ACCEPT}
    Add ESTABLISHED, to allow replies of outgoing connections you intiated!

@@

      \small{-A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT}

@@

      \small{-A INPUT -p tcp -m tcp -s 10.100.2.3 --dport 22 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.4 --dport 22 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.7 --dport 22 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.3 --dport 10000 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.4 --dport 10000 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.7 --dport 10000 -j ACCEPT}

@@

      \small{-N admin\_IP\\

@@

      -A admin\_IP -s 10.100.2.3 -j ACCEPT\\
      -A admin\_IP -s 10.100.2.4 -j ACCEPT\\
      -A admin\_IP -s 10.100.2.7 -j ACCEPT\\
      -A admin\_IP -j DROP}

@@

      \small{-A INPUT -p tcp -m tcp --dport 22 -j admin\_IP\\
      -A INPUT -p tcp -m tcp --dport 10000 -j admin\_IP}

@@

      \small{-N webmaster\_IP\\
      -A webmaster\_IP -s 10.100.2.11 -j ACCEPT\\
      -A webmaster\_IP -s 10.100.2.17 -j ACCEPT\\
      -A webmaster\_IP -s 10.100.2.34 -j ACCEPT\\
      -A webmaster\_IP -j DROP}

@@

      \small{-A INPUT -p tcp -m tcp --dport 445 -j admin\_IP\\
      -A INPUT -p tcp -m tcp --dport 445 -j webmaster\_IP\\
      -A INPUT -p tcp -m tcp --dport 139 -j admin\_IP\\
      -A INPUT -p tcp -m tcp --dport 139 -j webmaster\_IP}

@@

      \small{-N webmaster\_IP\\
      -A webmaster\_IP -s 10.100.2.11 -j ACCEPT\\
      -A webmaster\_IP -s 10.100.2.17 -j ACCEPT\\
      -A webmaster\_IP -s 10.100.2.34 -j ACCEPT\\
      \sout{-A webmaster\_IP -j DROP}\\
      -A webmaster\_IP -j admin\_IP}

@@

      \small{\sout{-A INPUT -p tcp -m tcp --dport 445 -j admin\_IP}\\
      -A INPUT -p tcp -m tcp --dport 445 -j webmaster\_IP\\
      \sout{-A INPUT -p tcp -m tcp --dport 139 -j admin\_IP}\\
      -A INPUT -p tcp -m tcp --dport 139 -j webmaster\_IP}
